---
title: "Survival Analysis of OV with Taxol, Taxotere, Carboplatin and Cisplatin"
output:
  pdf_document:
    fig_width: 7
    fig_height: 5
    fig_caption: true
---

# This is for survival analysis of OV data from TCGA.
Date: 04/14/2015

583 patients in total.

Time measured by month.

```{r, echo=FALSE}
library(survival)
library(GGally)
surv = read.table("/Users/zhenyu/Downloads/working/Steph/ov/surv.txt", h=T, sep="\t")
```

## 1. KM Curve and Survial test by Taxol:

```{r}
surv.data = with(surv, Surv(months,death) ~ taxol)
ggsurv(survfit(surv.data))
survdiff(surv.data)
```
___

## 2. KM Curve and Survial test by Taxotere:

```{r}
surv.data = with(surv, Surv(months,death) ~ taxotere)
ggsurv(survfit(surv.data))
survdiff(surv.data)
```
___

## 3. KM Curve and Survial test by Carboplatin:

```{r}
surv.data = with(surv, Surv(months,death) ~ carboplatin)
ggsurv(survfit(surv.data))
survdiff(surv.data)
```

___

## 4. KM Curve and Survial test by Cisplatin:

```{r}
surv.data = with(surv, Surv(months,death) ~ cisplatin)
ggsurv(survfit(surv.data))
survdiff(surv.data)
```

___

## 5. KM Curve and Survial test by Carboplatin or Cisplatin:

```{r}
surv.data = with(surv, Surv(months,death) ~ (carboplatin|cisplatin))
ggsurv(survfit(surv.data))
survdiff(surv.data)
```

___

## 6. KM Curve and Survial test by Taxol or Taxotere:

```{r}
surv.data = with(surv, Surv(months,death) ~ (taxol|taxotere))
ggsurv(survfit(surv.data))
survdiff(surv.data)
```

___

## 7. KM Curve and Survial test by at least one "Tax" and one "Platin":

```{r}
surv.data = with(surv, Surv(months,death) ~ ((carboplatin|cisplatin) & (taxol|taxotere)))
ggsurv(survfit(surv.data))
survdiff(surv.data)
```



